ARuko and Editour: \\ A Platform for Augmented Reality Tour Guide Apps

### 2019-10-05 paper.tex
edits to send in before ralph reads this over weekend

Since the frontend of Editour was implemented using basic web technologies, we
had access to the full power of CSS to style each element of the GUI. The
classes within CSS were designed so they could be reused easily and composed
with one another. If, for example, we needed to change the font of every element
that was styled like a button, we could do so by simply changing the
\texttt{font-family} attribute in a single CSS class. Consider the green bar
pictured in Figure~\ref{fig:mediaSubcard}. Multiple CSS classes were composed in
order to inherit the visual descriptions of other UI elements. The four CSS
classes on this bar are \texttt{button}, \texttt{greenbutton},
\texttt{outlinebutton}, and \texttt{revealer}. The class \texttt{button} styles
elements as the slightly raised, rounded rectangle that can be seen throughout
the UI. Additionally, all elements with the \texttt{button} class will have a
subtle ``press'' animation when being clicked on, since key frame animations can
also be defined in CSS. The default color of the button is red; the bottom of
the button is a slightly darker shade to give a 3D effect. Both of these colors
are conveniently stored as custom CSS variables, \texttt{--bg-color} and
\texttt{--bottom-color}. This allows another class to easily override these
colors. This is what the class \texttt{greenbutton} does; an HTML element with
the \texttt{button} class and either \texttt{greenbutton}, \texttt{orangebutton}
or \texttt{bluebutton} will be styled like a button and have a new color palette
applied. In order to differentiate the buttons that reveal subcards, the
\texttt{outlinebutton} class is used. This class takes the custom
\texttt{--bg-color} property and applies it to the border, drop shadow and text
color instead of the background. This class was also applied to the buttons that
can be seen in Figures~\ref{fig:jumpCard}~and~\ref{fig:downloadCard}. Finally,
the \texttt{revealer} class changes the text from centered to left-justified
among other minor formatting adjustments. CSS allowed us to define the look and
feel programmatically with the need to create graphical assets using image
editing software. This means that anyone using the codebase of Editour for
different purposes can easily change the look and feel of the frontend by
changing the CSS.\footnote{This is allowed since Editour is free software, which
is discussed briefly in Section~\ref{sec:futureOfEditour}.}

@@

When a user submits new tour from the web application, the files and metadata
are sent to the server running the Node.js scripts. The server zips up the files
and saves them to the disk with a timestamp. Then any application can request a
particular tour and the backend will serve the most recent version.

@@

Another notable change can be seen in the first screen on
Figure~\ref{fig:adobeXdDesign}. Atticus was not enthusiastic about being able
to place images onto the ground-plane using the AR camera. Instead, he
suggested that we have the images be viewable in a more traditional
fashion---in 2D as part of the UI.

@@

On the same screen, there is a scrollable window of text for a transcript of
the audio. Because of this, the Editour UI and tour metadata JSON file needed
to be updated to accommodate one transcript per region. On top of this, the C\#
code that interprets the tour file needed to be updated to expect an audio
transcript field.  Figure~\ref{fig:editourAdditions} shows the UI elements that
changed in order to add these new features.

@@

With the ground-plane detection features stripped away from the main app, the
AR focus shifted to translating the maps and signs using the camera. The fourth
screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
Atticus took photographs of various signs throughout Kinkaku-ji for us to use
as image targets. Hikaru Inoue helped us by translating all of the text in
these photos from Japanese to English. In this design, the AR camera
superimposes an ``info'' button on top of the sign. Tapping on this button
brings up a separate UI element containing the translation, which can be seen
in Figure~\ref{fig:signTranslation}. The details of this feature is discussed
more thoroughly in Section~\ref{sec:translationFeature}.

\begin{figure}[h] \centering
    \includegraphics[width=0.3\textwidth]{sign-translation.png}
    \caption{Translated sign using AR camera}
    \label{fig:signTranslation}
\end{figure}

Since Adobe XD is largely a prototyping and design tool, a considerable amount
of legwork would still need to be done to rebuild the proposed design using
Unity's UI components. Adobe XD allowed us to export a few important UI
elements as PNGs, such as the buttons to enter AR mode and view the map. We
briefly explored a few solutions to automating the task of getting the Adobe XD
project into Unity. We found one paid extension (for \$18) on the Unity Asset
store called ``Experience Importer - Adobe Xd files importer.'' The download
page for this extension claims ``Transfer AdobeXd project directly to Unity.
Forget about hours of positioning objects. They're already there! Just drag .xd
file to project and...  voila!''~\autocite{glasseye2019}.  We suspect this
sounds too good to be true because it is. As of September
20\textsuperscript{th}, 2019, there are 6 user reviews. All of the five-star
reviews were have the caveat ``Reviewer was gifted package by publisher'' which
which we interpreted as a warning sign. Because of this, we decided to rebuild
the UI largely from the ground up, using the Adobe XD file to guide us.
%TODO refer to the section that discusses building the ui

@@

We were presented with a set of equations that defined the mathematical model of
the heart we would be using to drive our physical model. Along with the
differential equations, we were also given an analogous circuit model that could
also be described by the same equations. The circuit and the equations can be
seen in Figure~\ref{fig:referenceModel}. We were also provided with source code
for an implementation of this model in C. We would still need to modify this
code to calculate the output variables we would need to properly operate the
physical model, and integrate the model into the main loop of the Arduino source
code with the appropriate timing.

>>>>

Since the frontend of Editour was implemented using basic web technologies, we
had access to the full power of cascading style sheets (CSS) to style each
element of the GUI. CSS is a style sheet language, meaning that it works in
tandem with markup languages like HTML, which define the structure of content on
the page~\autocite{mozillahtml2019}. CSS allows developers to define a set of
rules that describes how the content will look~\autocite{mozillacss2019}.

The classes within CSS were designed so they could be reused
easily and composed with one another. If, for example, we needed to change the
font of every element that was styled like a button, we could do so by simply
changing the \texttt{font-family} attribute in a single CSS class. Consider the
green bar pictured in Figure~\ref{fig:mediaSubcard}. Multiple CSS classes were
composed in order to inherit the visual descriptions of other UI elements. The
four CSS classes on this bar are \texttt{button}, \texttt{greenbutton},
\texttt{outlinebutton}, and \texttt{revealer}. The class \texttt{button} styles
elements as the slightly raised, rounded rectangle that can be seen throughout
the UI. Additionally, all elements with the \texttt{button} class will have a
subtle ``press'' animation when being clicked on, since key frame animations can
also be defined in CSS. The default color of the button is red; the bottom of
the button is a slightly darker shade to give a 3D effect. Both of these colors
are conveniently stored as custom CSS variables, \texttt{--bg-color} and
\texttt{--bottom-color}. This allows another class to easily override these
colors. This is what the class \texttt{greenbutton} does; an HTML element with
the \texttt{button} class and either \texttt{greenbutton}, \texttt{orangebutton}
or \texttt{bluebutton} will be styled like a button and have a new color palette
applied. In order to differentiate the buttons that reveal subcards, the
\texttt{outlinebutton} class is used. This class takes the custom
\texttt{--bg-color} property and applies it to the border, drop shadow and text
color instead of the background. This class was also applied to the buttons that
can be seen in Figures~\ref{fig:jumpCard}~and~\ref{fig:downloadCard}. Finally,
the \texttt{revealer} class changes the text from centered to left-justified
among other minor formatting adjustments. CSS allowed us to define the look and
feel programmatically with the need to create graphical assets using image
editing software. This means that anyone using the codebase of Editour for
different purposes can easily change the look and feel of the frontend by
changing the CSS.\footnote{This is allowed since Editour is free software, which
is discussed briefly in Section~\ref{sec:futureOfEditour}.}

@@

When a user submits new tour from the web application, the files and metadata
are sent to the server running the Node.js scripts. The server zips up the files
and saves them to the disk with a time stamp. Then any application can request a
particular tour and the backend will serve the most recent version.

@@

Another notable change can be seen in the first screen on
Figure~\ref{fig:adobeXdDesign} and Figure~\ref{fig:galleryZoomed}. Atticus was
not enthusiastic about being able to place images onto the ground-plane using
the AR camera. Instead, he suggested that we have the images be viewable in a
more traditional fashion---in 2D as part of the UI.

@@

% "scrollable" is for sure a neologism but let's normalize it through usage
On the same screen, there is a scrollable window of text for a transcript of
the audio. Because of this, the Editour UI and tour metadata JSON file needed
to be updated to accommodate one transcript per region. On top of this, the C\#
code that interprets the tour file needed to be updated to expect an audio
transcript field.  Figure~\ref{fig:editourAdditions} shows the UI elements that
changed in order to add these new features.

@@

With the ground-plane detection features stripped away from the main app, the AR
focus shifted to translating the maps and signs using the camera. The fourth
screen on Figure~\ref{fig:adobeXdDesign} and Figure~\ref{fig:infoZoomed} shows a
mock-up of this feature. Atticus took photographs of various signs throughout
Kinkaku-ji for us to use as image targets. Hikaru Inoue helped us by translating
all of the text in these photos from Japanese to English. In this design, the AR
camera superimposes an ``info'' button on top of the sign. Tapping on this
button brings up a separate UI element containing the translation, which can be
seen in Figure~\ref{fig:translationZoomed}. The details of this feature is
discussed more thoroughly in Section~\ref{sec:translationFeature}.

Since Adobe XD is largely a prototyping and design tool, a considerable amount
of legwork would still need to be done to rebuild the proposed design using
Unity's UI components. Adobe XD allowed us to export a few important UI elements
as PNGs, such as the buttons to enter AR mode and view the map. We briefly
explored a few solutions to automating the task of getting the Adobe XD project
into Unity. We found one paid extension (for \$18) on the Unity Asset store
called ``Experience Importer - Adobe Xd files importer.'' The download page for
this extension claims ``Transfer AdobeXd project directly to Unity. Forget about
hours of positioning objects. They're already there! Just drag .xd file to
project and... voila!''~\autocite{glasseye2019}.\footnote{``Adobe XD'' is
stylized incorrectly with ``AdobeXd'' in the description of the Unity
package. This is also different from ``Adobe Xd'', the way in which it is
stylized in the title.} We suspect this sounds too good to be true because it
is. As of September 20\textsuperscript{th}, 2019, there are 6 user reviews. All
of the five-star reviews were have the caveat ``Reviewer was gifted package by
publisher'' which which we interpreted as a warning sign. Because of this, we
decided to rebuild the UI largely from the ground up, using the Adobe XD file to
guide us.
%TODO refer to the section that discusses building the ui

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{chapters-zoomed.png}
    \caption{Larger screenshot of the chapter selection screen mock-up}
    \label{fig:chaptersZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{gallery-zoomed.png}
    \caption{Larger screenshot of the transcript and image gallery mock-up}
    \label{fig:galleryZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{info-zoomed.png}
    \caption{Larger screenshot of the info button mock-up}
    \label{fig:infoZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{map-zoomed.png}
    \caption{Larger screenshot of the route screen mock-up}
    \label{fig:mapZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{translation-zoomed.png}
    \caption{Larger screenshot of the translation window mock-up}
    \label{fig:translationZoomed}
\end{figure}

@@

We were presented with a set of equations that defined the mathematical model of
the heart we would be using to drive our physical model. Along with the
differential equations, we were also given an analogous circuit model that could
also be described by the same equations. The circuit and the equations can be
seen in Figure~\ref{fig:referenceModel}. We were also provided with source code
for an implementation of this model in C. We would still need to modify this
code to calculate the output variables we would need to properly operate the
physical model and integrate the model into the main loop of the Arduino source
code with the appropriate timing.
